\addcontentsline{toc}{chapter}{Bibliografía}

\subsubsection*{Bibliografía artículos:}

\bibitem{} ``React Stateless Functional Components: Nine Wins You Might Have Overlooked''. Cory House, 29/03/2016. \url{https://hackernoon.com/react-stateless-functional-components-nine-wins-you-might-have-overlooked-997b0d933dbc}
\bibitem{} ``React-redux 'connect' explained ''. Soham Kaman, 31/03/2017. \url{https://www.sohamkamani.com/blog/2017/03/31/react-redux-connect-explained/}
\bibitem{} ``The Definitive Guide for building REST APIs''. Cléber Zavadniak, 10/06/2017. \url{https://medium.com/clebertech-en/the-definitive-guide-for-building-rest-apis-f70d37b1d656}
\bibitem{} ``React Binding Patterns: 5 Approaches for Handling `this`''. Cory House, 17/08/2016. \url{https://medium.freecodecamp.org/react-binding-patterns-5-approaches-for-handling-this-92c651b5af56}
\bibitem{} ``How Virtual-DOM and diffing works in React''. Gethyl George Kurian, 24/01/2017. \url{https://medium.com/@gethylgeorge/how-virtual-dom-and-diffing-works-in-react-6fc805f9f84e}
\bibitem{} ``MongoDB Schema Design: Relationships.''. 	William Zola, 29/05/2014.\url{https://www.mongodb.com/blog/post/6-rules-of-thumb-for-mongodb-schema-design-part-1}
\bibitem{} ``MongoDB Schema Design: Two-way referencing and denormalization''. William Zola, 06/06/2014.\url{https://www.mongodb.com/blog/post/6-rules-of-thumb-for-mongodb-schema-design-part-2}
\bibitem{} ``MongoDB Schema Design: Your guide through the rainbow''. William Zola, 11/06/2014.\url{https://www.mongodb.com/blog/post/6-rules-of-thumb-for-mongodb-schema-design-part-3}
\bibitem{} ``The 100\% correct way to structure a React app (or why there’s no such thing)''.David Gilbertson, 01/10/2017. \url{https://hackernoon.com/the-100-correct-way-to-structure-a-react-app-or-why-theres-no-such-thing-3ede534ef1ed}
\bibitem{} ``ReactJS Authentication Tutorial''. Prosper Otemuyiwa, 21/02/2017.\url{https://auth0.com/blog/reactjs-authentication-tutorial/}
\bibitem{} ``You Don't Know JS (book series)''. Kyle Simpson, 01/03/2014. \url{https://github.com/getify/You-Dont-Know-JS}
\bibitem{} ``ES6 Promises: Patterns and Anti-Patterns''. Bobby Brennan, 25/09/2017. \url{https://medium.com/datafire-io/es6-promises-patterns-and-anti-patterns-bbb21a5d0918}
\bibitem{} ``Docker Networking- How to connect multiple containers''. Osita Chibuike, 16/11/2017. \url{https://dev.to/mozartted/docker-networking--how-to-connect-multiple-containers-7fl}
\bibitem{} ``The Anatomy of a JSON Web Token''. Chris Sevilleja, 22/01/2015. \url{https://scotch.io/tutorials/the-anatomy-of-a-json-web-token}
\bibitem{} ``IBM: Get a grip on your JavaScript application state''. David Geary, 18/07/2016. \url{https://www.ibm.com/developerworks/library/wa-manage-state-with-redux-p1-david-geary/index.html}
\bibitem{} ``Webpack & The Hot Module Replacement''. Rajaraodv, 24/04/2016. \url{https://medium.com/@rajaraodv/webpack-hot-module-replacement-hmr-e756a726a07}

\bigskip
\subsubsection*{Bibliografía software más consultada:}
\bibitem{NJS} {\tt Node.js}. \url{https://nodejs.org/api/}
\bibitem{NPM} {\tt NPM}. \url{https://docs.npmjs.com/}
\bibitem{TCI} {\tt Travis CI}. \url{http://docs.travis-ci.com/}
\bibitem{Jest}. {\tt Jest}.  \url{https://facebook.github.io/jest/}
\bibitem{ReactJS}. {\tt React.js}.  \url{https://reactjs.org/}
\bibitem{Auth0}. {\tt Auth0}.  \url{https://auth0.com/docs}
\bibitem{Express.js}. {\tt Express.js}.  \url{http://expressjs.com/es/}
\bibitem{Material-UI}. {\tt Material-UI}.  \url{https://material-ui.com/}
\bibitem{Redux}. {\tt Redux}.  \url{https://es.redux.js.org/}
\bibitem{React-Router}. {\tt React-Router}.  \url{https://reacttraining.com/react-router/core/guides/philosophy}
\bibitem{Webpack}. {\tt Webpack}. \url{https://webpack.js.org}


\bigskip
\subsubsection*{Otra bibliografía:}
\begin{itemize}
  \item Consultas puntuales a la documentación de todos los servicios y dependencias.
	\item Consultas puntuales a {\tt Stack OverFlow}.
	\item Material docente asignaturas de la \textbf{Universidad de Granada}.
\end{itemize}
